% Chapter 4 — bilingual terminology for AI-agent workflows (Hebrew--English BiDi).

\begin{chapterintrobox}
AI-agent workflows are often designed in English, while local teams may document decisions,
approvals, and operational policy in Hebrew. This chapter defines shared terminology for
automation, supervision, and real work across both languages \cite{mediumworkflowagents}.
\end{chapterintrobox}

\section{Why Bilingual Terminology Matters}
\label{sec:bidi-why}

English dominates vendor documentation, model APIs, and agent-framework vocabulary. Yet
organizations that automate real work must explain credentials, review gates, and escalation
rules to Hebrew-speaking operators and managers. Without aligned terms, teams misread what
an \emph{Agent}, \emph{Task}, or \emph{Process} actually authorizes in production
\cite{arxiv2506workagents}.

Live workforce research asks which occupational tasks workers are willing to delegate to
agents versus keep under direct human control \cite{arxiv2506workagents}. Bilingual
terminology is therefore not cosmetic---it is how mixed-language teams agree on boundaries
before automation scales \cite{recomaijobroles}.

\section{Core English--Hebrew Terminology}
\label{sec:bidi-glossary}

When teams introduce AI agents into real work, they need shared terms for what the agent
can do, which tools it may use, and when a human must approve the result. The terms below
connect common English vocabulary from agent platforms with Hebrew wording that can be used
in local documentation and team discussions.

\vspace{0.35em}
\begin{itemize}
\item \textbf{Agent} --- \texthebrew{סוכן} --- Software component that performs a bounded work task using approved tools.
\item \textbf{Task} --- \texthebrew{משימה} --- A clear unit of work that can be assigned, reviewed, and measured.
\item \textbf{Workflow} --- \texthebrew{תהליך עבודה} --- The ordered path from request to final approved output.
\item \textbf{Tool} --- \texthebrew{כלי} --- An external service or function the agent may call during the task.
\item \textbf{API Key} --- \texthebrew{מפתח גישה} --- A credential that must be protected and never exposed in prompts or logs.
\item \textbf{Human-in-the-loop} --- \texthebrew{בקרה אנושית} --- Human approval before sensitive or high-risk output is accepted.
\end{itemize}

\section{Controlled Mixed-Language Communication}
\label{sec:bidi-mixed}

\begin{insightbox}{Mixed-language example}
\textbf{Mixed-language example.} In an Israeli engineering team, a design review might use
English terms such as Agent, Task, API Key, and Human-in-the-loop, while the operational
policy is explained in Hebrew.
\end{insightbox}

\noindent
The English labels above are standard in agent platforms. The operational policy itself can
be stated in Hebrew without embedding those Latin tokens inside Hebrew sentences.

\vspace{0.35em}
\begin{hebrew}
\begin{flushright}
בדיון פנימי, הצוות מפרט את מדיניות הפעולה בעברית ומגדיר מתי נדרש אישור אנושי.
\end{flushright}
\end{hebrew}

This example shows how mixed-language teams can keep platform terminology stable while
making the actual operating rules clear to local users. The important point is not the
language choice itself, but whether the team understands when the agent may continue, when
it must stop, and when human approval is required \cite{redditcomplextasks,mediumworkflowagents}.

\label{sec:bidi-hebrew-summary}

\begin{tcolorbox}[colback=boxBg,colframe=boxFrame,title={\texthebrew{סיכום בעברית}},sharp corners,halign title=flush right]
\begin{hebrew}
\begin{flushright}
סוכני בינה מלאכותית יכולים לבצע משימות מוגדרות בתוך תהליך עבודה מסודר.\\[0.45em]
במערכת כזו, המשימה מחולקת לשלבים קטנים וברורים, והסוכן משתמש בכלים כדי לאסוף מידע, ליצור טיוטה או לבצע פעולה מוגדרת.\\[0.45em]
כאשר המשימה רגישה, מסוכנת או לא ברורה, נדרשת בקרה אנושית לפני אישור התוצאה.\\[0.45em]
המטרה אינה להחליף בני אדם לגמרי, אלא להעביר משימות מובנות לאוטומציה תוך שמירה על אחריות, פיקוח ואיכות.\\[0.45em]
לכן חשוב להגדיר מראש מתי הסוכן יכול לפעול באופן עצמאי, ומתי נדרש אישור אנושי.
\end{flushright}
\end{hebrew}
\end{tcolorbox}

\section{Operational Guidance for Mixed-Language Teams}
\label{sec:bidi-practical}

When Hebrew-English teams deploy agents into real work, three practices keep automation safe:
\begin{itemize}
  \item Publish the terminology definitions in design reviews so every role shares the same
    workflow vocabulary.
  \item Store credentials and API access rules in a single authoritative runbook language,
    with Hebrew summaries where operators require them.
  \item Mark customer-facing and compliance-sensitive steps as human-in-the-loop regardless
    of language \cite{redditcomplextasks,recomaijobroles}.
\end{itemize}

\begin{warningbox}{Accountability before scale}
Automation can accelerate structured tasks in any language context, but approval language
must be explicit before agents act on consequential work \cite{arxiv2506workagents}.
\end{warningbox}
